\documentclass[twoside,11pt]{article}

% Any additional packages needed should be included after jmlr2e.
% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
% is archived at http://www.jmlr.org/format/natbib.pdf

\usepackage{jmlr2ecover}
\input{packages}
\input{commands}

% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}

% \jmlrheading{xx}{2018}{xx-xx}{9/18}{xx/xx}{gabava18}{Guillaume Gautier, R\'emi Bardenet, and Michal Valko}

% Short headings should be running head and authors last names

% \ShortHeadings{\DPPy}{Gautier, Bardenet, and Valko}

\begin{document}

\title{\emph{Cover letter}\\[1em]
\DPPy: Sampling Determinantal Point Processes with Python}

\author{\name Guillaume Gautier$^{*,\dagger}$ \email g.gautier@inria.fr \\
       \name R\'emi Bardenet$^\dagger$ \email remi.bardenet@gmail.com \\
       \name Michal Valko$^*$ \email michal.valko@inria.fr\\
       \addr $^*$SequeL team, INRIA Lille - Nord Europe,  40, avenue Halley 59650, Villeneuve d'Ascq, France\\
       \addr $^\dagger$Univ.\,Lille, CNRS, Centrale Lille, UMR 9189 - CRIStAL, 59651 Villeneuve d'Ascq, France
}

% \editor{}

\maketitle

\vspace{4em}

\pagenumbering{gobble}
\setcounter{footnote}{3}

Dear Editorial Board,\\

We submit the \DPPy\ Python library to the machine learning open source software (MLOSS) section of the Journal of Machine Learning Research.

\todo{(gg) Add purpose of DPPy}

The project is hosted on GitHub\footnote{\url{https://github.com/guilgautier/DPPy}} and supported by an extensive documentation\footnote{\url{https://dppy.readthedocs.io}} which provides the essential mathematical background and illustrates some key properties of DPPs through \DPPy\ objects and their methods.
We use Travis\footnote{\url{https://travis-ci.com/guilgautier/DPPy}} for continuous integration and to certify that \DPPy\ runs on Linux and MacOS plateforms with Python 3.4+.\\

In line with the reproducibily purpose, \DPPy\ does not rely on any proprietary software and is released under the MIT license.
Moreover, the companion paper\footnote{\url{https://github.com/guilgautier/DPPy_paper}} together with the present cover letter are also available on GitHub and fully reproducible.

\begin{itemize}
  \item \todo{(gg) should we give a brief explaination about how it is done with Travis ?}
  \item \todo{(gg) tag final commit of DPPy\_paper to create a release through Travis}\\
\end{itemize}

We declare that this work is neither published nor submitted to any journal or conference.
All authors agree to the reviewing process of the Journal of Machine Learning Research.
We declare no conflict of interest whatsoever.\\

Thank you for your consideration.\\

Mr. Guillaume Gautier (Ph.D. student)\\
\indent Dr. Rémi Bardenet (Research scientist)\\
\indent Dr. Michal Valko (Research scientist)\\

Version to be reviewed: \DPPy\ \href{https://github.com/guilgautier/DPPy}{v0.1.0}
\todo{(gg) tag final commit of DPPy to create a release through Travis}\\

\end{document}